Structured Versus Decorated Cospans

### 2020-12-07 cospans.tex
Fixing small typos mainly in Appendix B

\& F(m_1)\times F(n_2)\times F(m_2)\times F(n_2)\ar[dd,"1\times\beta\times1"]\ar[ddrr,phantom,"\cong"]\ar[rr,"\phi_{m_1,n_1}\times\phi_{m_2,n_2}"] \&\& F(m_1+n_1)\times F(m_2+n_2)\ar[rr,"\phi_{m_1+n_1,m_2+n_2}"] \&\& F(m_1+n_1+m_2+n_2)\ar[dd,"F\psi"]\ar[ddll,"F(1\times\beta\times1)"'] \\

@@

Let us now sketch the story; details will appear in a forthcoming paper \cite{CV}.  Suppose the conditions hold for constructing the double category of structured cospans ${}_L \lCsp(\X)$ as in \cref{thm:SC}.  That is, suppose $\A$ and $\X$ have finite colimits and $L \maps \A \to \X$ preserves them.    If $L$ also has a right adjoint `left inverse' (meaning the unit is the identity) $U \maps \X \to \A$, which moreover strictly preserves the chosen pushouts, it can be shown that $U$ is an opfibration.  Consequently, $U$ corresponds to a pseudofunctor $F \maps \A \to \Cat$ by the inverse Grothendieck construction, as in the first part of \cref{thm:Grothendieck}. Furthermore, if $U$ preserves finite coproducts, $F$ acquires the structure of a lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat,\times)$ by the special case of the cocartesian monoidal Grothendieck construction discussed under \cref{lem:MonGroth}.  As a result, $F$ has now enough structure to induce a double category of decorated cospans $F\lCsp$  as in \cref{DC}.  Finally, it can be shown that the structured and decorated cospan double categories categories are equivalent as symmetric monoidal double categories: ${}_L \lCsp(\X) \simeq F\Csp$.

@@

Here we show a sample check of a coherence law for the proof of \cref{DC}.
All relevant structure for decorated cospans is as described in \cref{thm:decorated_cospans,DC}. The coherence law that we check says that this diagram commutes:
\begin{equation}\label{eq:thisdiagram}
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$(M_2 \otimes N_2) \odot (M_1 \otimes N_1)$};
\node (B) at (3,0) {$(N_2 \otimes M_2) \odot (N_1 \otimes M_1)$};
\node (C) at (0,-.75) {$(M_2 \odot M_1) \otimes (N_2 \odot N_1)$};
\node (D) at (3,-.75) {$(N_2 \odot N_1) \otimes (M_2 \odot M_1)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\beta \odot \beta$} (B)
(B) edge node[right]{$\chi$} (D)
(A) edge node[left]{$\chi$} (C)
(C) edge node[above]{$\beta$} (D);
\end{tikzpicture}
\end{equation}
where $M_1,M_2,N_1,N_2$ are as in \cref{eq:4deccospans}, $\chi$ is as described right below therein and $\beta$ is the braiding defined as in \cref{eq:braidingFCsp1} -- although the letter $\beta$ is also used for the braiding in $\A$.
First of all, if we only consider the underlying cospans without their decorations, we obtain the following `flattened' commutative diagram in $\A$ -- which verifies the corresponding axiom for the symmetric monoidal double category $\lCsp(\A)$:
%%% Kenny any good reference for that? Not just cospans, which I can find in Niefield, but the interchange law as well for cospans only. Is it in your thesis? Somewhere in Shulman? Had a look but couldn't dig up anything...I know it is easy but would look nicer if we had some reference here
\[
		\begin{tikzpicture}
			\node (a) at (-4,0) {$a+a'$};
			\node (b) at (1,0) {$(m_1+n_1) +_{(b+b')} (m_2+n_2)$};
			\node (c) at (6,0) {$c+c'$};
			\node (a2) at (-4,1) {$a'+a$};
			\node (b2) at (1,1) {$(n_1+m_1) +_{(b'+b)} (n_2+m_2)$};
			\node (c2) at (6,1) {$c'+c$};
            \node (a3) at (-4,2) {$a'+a$};
			\node (b3) at (1,2) {$(n_1 +_{b'} n_2) + (m_1 +_b m_2)$};
			\node (c3) at (6,2) {$c'+c$};
            \node (a5) at (-4,-1) {$a+a'$};
			\node (b5) at (1,-1) {$(m_1+_b m_2) + (n_1+_{b'} n_2)$};
			\node (c5) at (6,-1) {$c+c'$};
            \node (a6) at (-4,-2) {$a'+a$};
			\node (b6) at (1,-2) {$(n_1 +_{b'} n_2) + (m_1 +_b m_2)$};
			\node (c6) at (6,-2) {$c'+c$};
			\path[->,font=\scriptsize,>=angle 90]
			(a) edge node[above]{$$} (b)
			(c) edge node[above]{$$} (b)
            (a2) edge node[above]{$$} (b2)
			(c2) edge node[above]{$$} (b2)
            (a) edge node[left]{$\beta$} (a2)
            (b) edge node[left]{$\beta +_\beta \beta$} (b2)
%(b) edge node[right]{$\tau_1$} (b2)
			(c) edge node[right]{$\beta$} (c2)
            (a3) edge node[above]{$$} (b3)
			(c3) edge node[above]{$$} (b3)
            (a2) edge node[left]{$1$} (a3)
            (b2) edge node[left]{$\hat{\chi}$} (b3)
%(b2) edge node[right]{$\tau_2$} (b3)
			(c2) edge node[right]{$1$} (c3)
            (a5) edge node[above]{$$} (b5)
			(c5) edge node[above]{$$} (b5)
            (a) edge node[left]{$1$} (a5)
            (b) edge node[left]{$\hat{\chi}$} (b5)
%(b) edge node[right]{$\tau_4$} (b5)
			(c) edge node[right]{$1$} (c5)
            (a6) edge node[above]{$$} (b6)
			(c6) edge node[above]{$$} (b6)
            (a5) edge node[left]{$\beta$} (a6)
            (b5) edge node[left]{$\beta$} (b6)
 %(b5) edge node[right]{$\tau_5$} (b6)
			(c5) edge node[right]{$\beta$} (c6);
		\end{tikzpicture}
	\]
The top and the bottom cospans coincide, and $\hat{\chi}$ is the canonical isomorphism by the universal property of colimits
%globular 2-morphism interchanging the tensor product and horizontal composition of the symmetric monoidal double category $\lCsp(\A)$,
and the inwards pointing morphisms are natural maps from the each cospan's feet to its apex.

@@

			\node (b) at (1,0) {$(m_1+n_1) +_{(b+b')} (m_2+n_2)$};
			\node (c) at (8,0) {$ (x_2\oplus y_2)\odot (x_1\oplus y_1)  \in F((m_1+n_1)+_{b+b'}(m_2+n_2))$};

@@

			\node (b2) at (1,1) {$(n_1+m_1) +_{(b'+b)} (n_2+m_2)$};
			\node (c2) at (8,1) {$(y_2\oplus x_2)\odot(y_1\oplus x_1) \in F((n_1+m_1)+_{b'+b}(n_2+m_2))$};

@@

			\node (b3) at (1,2) {$(n_1 +_{b'} n_2) + (m_1 +_b m_2)$};
			\node (c3) at (8,2) {$(y_2 \odot y_1) \oplus (x_2 \odot x_1) \in F((n_1+_{b'} n_2)+(m_1+_b m_2))$};

@@

			\node (b5) at (1,-1) {$(m_1+_b m_2) + (n_1+_{b'} n_2)$};
			\node (c5) at (8,-1) {$(x_2 \odot x_1) \oplus (y_2 \odot y_1) \in F((m_1+_b m_2)+(n_1+_{b'} n_2))$};

@@

			\node (b6) at (1,-2) {$(n_1 +_{b'} n_2) + (m_1 +_b m_2)$};
			\node (c6) at (8,-2) {$(y_2 \odot y_1) \oplus (x_2 \odot x_1) \in F((n_1+_{b'} n_2)+(m_1+_b m_2))$};

@@

\node (E) at (6.75,0.5) {$\scriptstyle{F(m_1 + n_1) \times F(m_2+n_2)}$};

@@

\node (E') at (6.75,-0.5) {$\scriptstyle{F(m_1+m_2) \times F(n_1+n_2)}$};
\node (B) at (9,0.5) {$\scriptstyle{F((m_1+n_1)+(m_2+n_2))}$};
\node (B') at (9,-0.5) {$\scriptstyle{F(m_1+_b m_2)\times F(n_1+_{b'}n_2)}$};
\node (C) at (11.5,0.5) {$\scriptstyle{F((m_1+n_1)+_{b+b'}(m_2+n_2))}$};
\node (C') at (11.5,-0.5) {$\scriptstyle{F((m_1+_b m_2)+ (n_1+_{b'} n_2))}$};
\node (G) at (4.25,0.5) {$\scriptstyle{F(m_1) \times F(n_1) \times F(m_2) \times F(n_2)}$};
\node (G') at (4.25,-0.5) {$\scriptstyle{F(m_1) \times F(m_2) \times F(n_1) \times F(n_2)}$};
\node (G'') at (4.25,-1.5) {$\scriptstyle{F(n_1) \times F(n_2) \times F(m_1) \times F(m_2)}$};
\node (E'') at (6.75,-1.5) {$\scriptstyle{F(n_1+n_2) \times F(m_1+m_2)}$};
\node (B'') at (9,-1.5) {$\scriptstyle{F(n_1+_{b'}n_2)+F(m_1+_b m_2)}$};
\node (C'') at (11.5,-1.5) {$\scriptstyle{F((n_1+_{b'}n_2)+(m_1+_b m_2))}$};
\node (X) at (3.4,0.2) {$\scriptscriptstyle{x_1 \times y_1 \times x_2 \times y_2}$};
\node (X') at (3.4,-0.35) {$\scriptscriptstyle{x_1 \times x_2 \times y_1 \times y_2}$};
\node (X'') at (3.4,-1.2) {$\scriptscriptstyle{y_1 \times y_2 \times x_1 \times x_2}$};

@@

(E) edge node [above] {$\phi_{m_1+n_1,m_2+n_2}$} (B)

@@

(B'') edge node [below] {$\phi_{n_1+_{b'}n_2,m_1+_bm_2}$} (C'')
(B') edge node [above] {$\phi_{m_1+_bm_2,n_1+_{b'}n_2}$} (C')

@@

(G) edge node [above] {$\phi_{m_1,n_1} {\times} \phi_{m_2,n_2}$} (E)
(G'') edge node [below] {$\phi_{n_1,n_2} {\times} \phi_{m_1,m_2}$} (E'')
(G') edge node [above] {$\phi_{m_1,m_2} \times \phi_{n_1,n_2}$} (E')

@@

\node (E') at (6.75,-0.5) {$\scriptstyle{F(m_1+m_2) \times F(n_1+n_2)}$};
\node (B) at (9,0.5) {$\scriptstyle{F((m_1+n_1)+(m_2+n_2))}$};
\node (B') at (9,-0.5) {$\scriptstyle{F((m_1+ m_2)+(n_1+n_2))}$};
\node (C) at (11.5,0.5) {$\scriptstyle{F((m_1+n_1)+_{b+b'}(m_2+n_2))}$};
\node (C') at (11.5,-0.5) {$\scriptstyle{F((m_1+_b m_2)+ (n_1+_{b'} n_2))}$};
\node (G) at (4.25,0.5) {$\scriptstyle{F(m_1) \times F(n_1) \times F(m_2) \times F(n_2)}$};
\node (G') at (4.25,-0.5) {$\scriptstyle{F(m_1) \times F(m_2) \times F(n_1) \times F(n_2)}$};
\node (G'') at (4.25,-1.5) {$\scriptstyle{F(n_1) \times F(n_2) \times F(m_1) \times F(m_2)}$};
\node (E'') at (6.75,-1.5) {$\scriptstyle{F(n_1+n_2) \times F(m_1+m_2)}$};
\node (B'') at (9,-1.5) {$\scriptstyle{F((n_1+n_2)+(m_1+ m_2))}$};
\node (C'') at (11.5,-1.5) {$\scriptstyle{F((n_1+_{b'}n_2)+(m_1+_b m_2))}$};
\node (X) at (3.4,0.2) {$\scriptscriptstyle{x_1 \times y_1 \times x_2 \times y_2}$};
\node (X') at (3.4,-0.35) {$\scriptscriptstyle{x_1 \times x_2 \times y_1 \times y_2}$};
\node (X'') at (3.4,-1.2) {$\scriptscriptstyle{y_1 \times y_2 \times x_1 \times x_2}$};

@@

(E) edge node [above] {$\phi_{m_1+n_1,m_2+n_2}$} (B)
(E'') edge node [above] {$\phi_{n_1+n_2,m_1+m_2}$} (B'')
(E') edge node [above] {$\phi_{m_1+m_2,n_1+n_2}$} (B')

@@

(G) edge node [above] {$\phi_{m_1,n_1} {\times} \phi_{m_2,n_2}$} (E)
(G'') edge node [above] {$\phi_{n_1,n_2} {\times} \phi_{m_1,m_2}$} (E'')
(G') edge node [above] {$\phi_{m_1,m_2} \times \phi_{n_1,n_2}$} (E')

@@

\node (E') at (6.75,-0.5) {$\scriptstyle{F(n_1+m_1) \times F(n_2+m_2)}$};
\node (B) at (9,0.5) {$\scriptstyle{F((m_1+n_1)+(m_2+n_2))}$};
\node (B') at (9,-0.5) {$\scriptstyle{F((n_1+m_1)+(n_2+m_2))}$};
\node (C) at (11.5,0.5) {$\scriptstyle{F((m_1+n_1)+_{b+b'}(m_2+n_2))}$};
\node (C') at (11.5,-0.5) {$\scriptstyle{F((n_1+m_1)+_{b'+b}(n_2+m_2))}$};
\node (G) at (4.25,0.5) {$\scriptstyle{F(m_1) \times F(n_1) \times F(m_2) \times F(n_2)}$};
\node (G') at (4.25,-0.5) {$\scriptstyle{F(n_1) \times F(m_1) \times F(n_2) \times F(m_2)}$};
\node (G'') at (4.25,-1.5) {$\scriptstyle{F(n_1) \times F(n_2) \times F(m_1) \times F(m_2)}$};
\node (E'') at (6.75,-1.5) {$\scriptstyle{F(n_1+n_2) \times F(m_1+m_2)}$};
\node (B'') at (9,-1.5) {$\scriptstyle{F(n_1+_{b'}n_2)+ F(m_1+_b m_2))}$};
\node (C'') at (11.5,-1.5) {$\scriptstyle{F((n_1+_{b'}n_2)+(m_1+_b m_2))}$};
\node (X) at (3.4,0.2) {$\scriptscriptstyle{x_1 \times y_1 \times x_2 \times y_2}$};
\node (X') at (3.4,-0.35) {$\scriptscriptstyle{y_1 \times x_1 \times y_2 \times x_2}$};
\node (X'') at (3.4,-1.2) {$\scriptscriptstyle{y_1 \times y_2 \times x_1 \times x_2}$};

@@

(E') edge node [above] {$\phi_{n_1+m_1,n_2+m_2}$} (B')

@@

(B'') edge node [below] {$\phi_{n_1+_{b'}n_2,m_1+_{b}m_2}$} (C'')

@@

(G) edge node [above] {$\phi_{m_1,n_1} {\times} \phi_{m_2,n_2}$} (E)
(G'') edge node [below] {$\phi_{n_1,n_2} {\times} \phi_{m_1,m_2}$} (E'')
(G') edge node [above] {$\phi_{n_1,m_1} \times \phi_{n_2,m_2}$} (E')

>>>>

\& F(m_1)\times F(n_1)\times F(m_2)\times F(n_2)\ar[dd,"1\times\beta\times1"]\ar[ddrr,phantom,"\cong"]\ar[rr,"\phi_{m_1,n_1}\times\phi_{m_2,n_2}"] \&\& F(m_1+n_1)\times F(m_2+n_2)\ar[rr,"\phi_{m_1+n_1,m_2+n_2}"] \&\& F(m_1+n_1+m_2+n_2)\ar[dd,"F\psi"]\ar[ddll,"F(1+\beta+1)"'] \\

@@

Let us now sketch the story; details will appear in a forthcoming paper \cite{CV}.  Suppose the conditions hold for constructing the double category of structured cospans ${}_L \lCsp(\X)$ as in \cref{thm:SC}.  That is, suppose $\A$ and $\X$ have finite colimits and $L \maps \A \to \X$ preserves them.    If $L$ also has a right adjoint `left inverse' (meaning the unit is the identity) $U \maps \X \to \A$, which moreover strictly preserves the chosen pushouts, it can be shown that $U$ is an opfibration.  Consequently, $U$ corresponds to a pseudofunctor $F \maps \A \to \Cat$ by the inverse Grothendieck construction, as in the first part of \cref{thm:Grothendieck}. Furthermore, if $U$ preserves finite coproducts, $F$ acquires the structure of a lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat,\times)$ by the special case of the cocartesian monoidal Grothendieck construction discussed under \cref{lem:MonGroth}.  As a result, $F$ has now enough structure to induce a double category of decorated cospans $F\lCsp$  as in \cref{DC}.  Finally, it can be shown that the structured and decorated cospan double categories are equivalent as symmetric monoidal double categories: ${}_L \lCsp(\X) \simeq F\lCsp$.

@@

Here we show a sample check of a coherence law for the proof of \cref{DC}.
All relevant structure for decorated cospans is as described in \cref{thm:decorated_cospans,DC}. The coherence law that we check says that this diagram commutes:
\begin{equation}\label{eq:thisdiagram}
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$(M_2 \otimes N_2) \odot (M_1 \otimes N_1)$};
\node (B) at (3,0) {$(N_2 \otimes M_2) \odot (N_1 \otimes M_1)$};
\node (C) at (0,-.75) {$(M_2 \odot M_1) \otimes (N_2 \odot N_1)$};
\node (D) at (3,-.75) {$(N_2 \odot N_1) \otimes (M_2 \odot M_1)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\beta \odot \beta$} (B)
(B) edge node[right]{$\chi$} (D)
(A) edge node[left]{$\chi$} (C)
(C) edge node[above]{$\beta$} (D);
\end{tikzpicture}
\end{equation}
where $M_1,M_2,N_1,N_2$ are as in \cref{eq:4deccospans}, $\chi$ is as described right below therein and $\beta$ is the braiding defined as in \cref{eq:braidingFCsp1} -- although the letter $\beta$ is also used for the braiding in $\A$.
First of all, if we only consider the underlying cospans without their decorations, we obtain the following `flattened' commutative diagram in $\A$ -- which verifies the corresponding axiom for the symmetric monoidal double category $\lCsp(\A)$:
%%% Kenny any good reference for that? Not just cospans, which I can find in Niefield, but the interchange law as well for cospans only. Is it in your thesis? Somewhere in Shulman? Had a look but couldn't dig up anything...I know it is easy but would look nicer if we had some reference here
\[
		\begin{tikzpicture}
			\node (a) at (-4,0) {$a+a'$};
			\node (b) at (1,0) {$(m_2+n_2) +_{(b+b')} (m_1+n_1)$};
			\node (c) at (6,0) {$c+c'$};
			\node (a2) at (-4,1) {$a'+a$};
			\node (b2) at (1,1) {$(n_2+m_2) +_{(b'+b)} (n_1+m_1)$};
			\node (c2) at (6,1) {$c'+c$};
            \node (a3) at (-4,2) {$a'+a$};
			\node (b3) at (1,2) {$(n_2 +_{b'} n_1) + (m_2 +_b m_1)$};
			\node (c3) at (6,2) {$c'+c$};
            \node (a5) at (-4,-1) {$a+a'$};
			\node (b5) at (1,-1) {$(m_2+_b m_1) + (n_2+_{b'} n_1)$};
			\node (c5) at (6,-1) {$c+c'$};
            \node (a6) at (-4,-2) {$a'+a$};
			\node (b6) at (1,-2) {$(n_2 +_{b'} n_1) + (m_2 +_b m_1)$};
			\node (c6) at (6,-2) {$c'+c$};
			\path[->,font=\scriptsize,>=angle 90]
			(a) edge node[above]{$$} (b)
			(c) edge node[above]{$$} (b)
            (a2) edge node[above]{$$} (b2)
			(c2) edge node[above]{$$} (b2)
            (a) edge node[left]{$\beta$} (a2)
            (b) edge node[left]{$\beta +_\beta \beta$} (b2)
%(b) edge node[right]{$\tau_1$} (b2)
			(c) edge node[right]{$\beta$} (c2)
            (a3) edge node[above]{$$} (b3)
			(c3) edge node[above]{$$} (b3)
            (a2) edge node[left]{$1$} (a3)
            (b2) edge node[left]{$\hat{\chi}$} (b3)
%(b2) edge node[right]{$\tau_2$} (b3)
			(c2) edge node[right]{$1$} (c3)
            (a5) edge node[above]{$$} (b5)
			(c5) edge node[above]{$$} (b5)
            (a) edge node[left]{$1$} (a5)
            (b) edge node[left]{$\hat{\chi}$} (b5)
%(b) edge node[right]{$\tau_4$} (b5)
			(c) edge node[right]{$1$} (c5)
            (a6) edge node[above]{$$} (b6)
			(c6) edge node[above]{$$} (b6)
            (a5) edge node[left]{$\beta$} (a6)
            (b5) edge node[left]{$\beta$} (b6)
 %(b5) edge node[right]{$\tau_5$} (b6)
			(c5) edge node[right]{$\beta$} (c6);
		\end{tikzpicture}
	\]
The top and the bottom cospans coincide, and $\hat{\chi}$ is the canonical isomorphism by the universal property of colimits
%globular 2-morphism interchanging the tensor product and horizontal composition of the symmetric monoidal double category $\lCsp(\A)$,
and the inwards pointing morphisms are natural maps from the each cospan's feet to its apex.

@@

			\node (b) at (1,0) {$(m_2+n_2) +_{(b+b')} (m_1+n_1)$};
			\node (c) at (8,0) {$ (x_2\oplus y_2)\odot (x_1\oplus y_1)  \in F((m_2+n_2)+_{b+b'}(m_1+n_1))$};

@@

			\node (b2) at (1,1) {$(n_2+m_2) +_{(b'+b)} (n_1+m_1)$};
			\node (c2) at (8,1) {$(y_2\oplus x_2)\odot(y_1\oplus x_1) \in F((n_2+m_2)+_{b'+b}(n_1+m_1))$};

@@

			\node (b3) at (1,2) {$(n_2 +_{b'} n_1) + (m_2 +_b m_1)$};
			\node (c3) at (8,2) {$(y_2 \odot y_1) \oplus (x_2 \odot x_1) \in F((n_2+_{b'} n_1)+(m_2+_b m_1))$};

@@

			\node (b5) at (1,-1) {$(m_2+_b m_1) + (n_2+_{b'} n_1)$};
			\node (c5) at (8,-1) {$(x_2 \odot x_1) \oplus (y_2 \odot y_1) \in F((m_2+_b m_1)+(n_2+_{b'} n_1))$};

@@

			\node (b6) at (1,-2) {$(n_2 +_{b'} n_1) + (m_2 +_b m_1)$};
			\node (c6) at (8,-2) {$(y_2 \odot y_1) \oplus (x_2 \odot x_1) \in F((n_2+_{b'} n_1)+(m_2+_b m_1))$};

@@

\node (E) at (6.75,0.5) {$\scriptstyle{F(m_2 + n_2) \times F(m_1+n_1)}$};

@@

\node (E') at (6.75,-0.5) {$\scriptstyle{F(m_2+m_1) \times F(n_2+n_1)}$};
\node (B) at (9,0.5) {$\scriptstyle{F((m_2+n_2)+(m_1+n_1))}$};
\node (B') at (9,-0.5) {$\scriptstyle{F(m_2+_b m_1)\times F(n_2+_{b'}n_1)}$};
\node (C) at (11.5,0.5) {$\scriptstyle{F((m_2+n_2)+_{b+b'}(m_1+n_1))}$};
\node (C') at (11.5,-0.5) {$\scriptstyle{F((m_2+_b m_1)+ (n_2+_{b'} n_1))}$};
\node (G) at (4.25,0.5) {$\scriptstyle{F(m_2) \times F(n_2) \times F(m_1) \times F(n_1)}$};
\node (G') at (4.25,-0.5) {$\scriptstyle{F(m_2) \times F(m_1) \times F(n_2) \times F(n_1)}$};
\node (G'') at (4.25,-1.5) {$\scriptstyle{F(n_2) \times F(n_1) \times F(m_2) \times F(m_1)}$};
\node (E'') at (6.75,-1.5) {$\scriptstyle{F(n_2+n_1) \times F(m_2+m_1)}$};
\node (B'') at (9,-1.5) {$\scriptstyle{F(n_2+_{b'}n_1) \times F(m_2+_b m_1)}$};
\node (C'') at (11.5,-1.5) {$\scriptstyle{F((n_2+_{b'}n_1)+(m_2+_b m_1))}$};
\node (X) at (3.4,0.2) {$\scriptscriptstyle{x_2 \times y_2 \times x_1 \times y_1}$};
\node (X') at (3.4,-0.35) {$\scriptscriptstyle{x_2 \times x_1 \times y_2 \times y_1}$};
\node (X'') at (3.4,-1.2) {$\scriptscriptstyle{y_2 \times y_1 \times x_2 \times x_1}$};

@@

(E) edge node [above] {$\phi_{m_2+n_2,m_1+n_1}$} (B)

@@

(B'') edge node [below] {$\phi_{n_2+_{b'}n_1,m_2+_b m_1}$} (C'')
(B') edge node [above] {$\phi_{m_2+_b m_1,n_2+_{b'}n_1}$} (C')

@@

(G) edge node [above] {$\phi_{m_2,n_2} {\times} \phi_{m_1,n_1}$} (E)
(G'') edge node [below] {$\phi_{n_2,n_1} {\times} \phi_{m_2,m_1}$} (E'')
(G') edge node [above] {$\phi_{m_2,m_1} \times \phi_{n_2,n_1}$} (E')

@@

\node (E') at (6.75,-0.5) {$\scriptstyle{F(m_2+m_1) \times F(n_2+n_1)}$};
\node (B) at (9,0.5) {$\scriptstyle{F((m_2+n_2)+(m_1+n_1))}$};
\node (B') at (9,-0.5) {$\scriptstyle{F((m_2+ m_1)+(n_2+n_1))}$};
\node (C) at (11.5,0.5) {$\scriptstyle{F((m_2+n_2)+_{b+b'}(m_1+n_1))}$};
\node (C') at (11.5,-0.5) {$\scriptstyle{F((m_2+_b m_1)+ (n_2+_{b'} n_1))}$};
\node (G) at (4.25,0.5) {$\scriptstyle{F(m_2) \times F(n_2) \times F(m_1) \times F(n_1)}$};
\node (G') at (4.25,-0.5) {$\scriptstyle{F(m_2) \times F(m_1) \times F(n_2) \times F(n_1)}$};
\node (G'') at (4.25,-1.5) {$\scriptstyle{F(n_2) \times F(n_1) \times F(m_2) \times F(m_1)}$};
\node (E'') at (6.75,-1.5) {$\scriptstyle{F(n_2+n_1) \times F(m_2+m_1)}$};
\node (B'') at (9,-1.5) {$\scriptstyle{F((n_2+n_1)+(m_2+ m_1))}$};
\node (C'') at (11.5,-1.5) {$\scriptstyle{F((n_2+_{b'}n_1)+(m_2+_b m_1))}$};
\node (X) at (3.4,0.2) {$\scriptscriptstyle{x_2 \times y_2 \times x_1 \times y_1}$};
\node (X') at (3.4,-0.35) {$\scriptscriptstyle{x_2 \times x_1 \times y_2 \times y_1}$};
\node (X'') at (3.4,-1.2) {$\scriptscriptstyle{y_2 \times y_1 \times x_2 \times x_1}$};

@@

(E) edge node [above] {$\phi_{m_2+n_2,m_1+n_1}$} (B)
(E'') edge node [above] {$\phi_{n_2+n_1,m_2+m_1}$} (B'')
(E') edge node [above] {$\phi_{m_2+m_1,n_2+n_1}$} (B')

@@

(G) edge node [above] {$\phi_{m_2,n_2} {\times} \phi_{m_1,n_1}$} (E)
(G'') edge node [above] {$\phi_{n_2,n_1} {\times} \phi_{m_2,m_1}$} (E'')
(G') edge node [above] {$\phi_{m_2,m_1} \times \phi_{n_2,n_1}$} (E')

@@

\node (E') at (6.75,-0.5) {$\scriptstyle{F(n_2+m_2) \times F(n_1+m_1)}$};
\node (B) at (9,0.5) {$\scriptstyle{F((m_2+n_2)+(m_1+n_1))}$};
\node (B') at (9,-0.5) {$\scriptstyle{F((n_2+m_2)+(n_1+m_1))}$};
\node (C) at (11.5,0.5) {$\scriptstyle{F((m_2+n_2)+_{b+b'}(m_1+n_1))}$};
\node (C') at (11.5,-0.5) {$\scriptstyle{F((n_2+m_2)+_{b'+b}(n_1+m_1))}$};
\node (G) at (4.25,0.5) {$\scriptstyle{F(m_2) \times F(n_2) \times F(m_1) \times F(n_1)}$};
\node (G') at (4.25,-0.5) {$\scriptstyle{F(n_2) \times F(m_2) \times F(n_1) \times F(m_1)}$};
\node (G'') at (4.25,-1.5) {$\scriptstyle{F(n_2) \times F(n_1) \times F(m_2) \times F(m_1)}$};
\node (E'') at (6.75,-1.5) {$\scriptstyle{F(n_2+n_1) \times F(m_2+m_1)}$};
\node (B'') at (9,-1.5) {$\scriptstyle{F(n_2+_{b'}n_1)\times F(m_2+_b m_1)}$};
\node (C'') at (11.5,-1.5) {$\scriptstyle{F((n_2+_{b'}n_1)+(m_2+_b m_1))}$};
\node (X) at (3.4,0.2) {$\scriptscriptstyle{x_2 \times y_2 \times x_1 \times y_1}$};
\node (X') at (3.4,-0.35) {$\scriptscriptstyle{y_2 \times x_2 \times y_1 \times x_1}$};
\node (X'') at (3.4,-1.2) {$\scriptscriptstyle{y_2 \times y_1 \times x_2 \times x_1}$};

@@

(E') edge node [above] {$\phi_{n_2+m_2,n_1+m_1}$} (B')

@@

(B'') edge node [below] {$\phi_{n_2+_{b'}n_1,m_2+_{b}m_1}$} (C'')

@@

(G) edge node [above] {$\phi_{m_2,n_2} {\times} \phi_{m_1,n_1}$} (E)
(G'') edge node [below] {$\phi_{n_2,n_1} {\times} \phi_{m_2,m_1}$} (E'')
(G') edge node [above] {$\phi_{n_2,m_2} \times \phi_{n_1,m_1}$} (E')
